%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{tikz}
\usepackage{graphicx}

\begin{document}

\header{Tim}{Fogarty}{student software engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
% \begin{tikzpicture}
% \node[align=center] {line one\\ line two} 
% \end{tikzpicture}
11 City Road
Nottingham
NG7 2JJ
United Kingdom
~
+44 7527061752
~
\href{mailto:timothy.fogo@gmail.com}{timothy.fogo@gmail.com}
\href{https://github.com/tfogo}{GH: github.com/tfogo}
Twitter: @tfogo
Stack Overflow: tfogo
\section{programming}
JavaScript 
(Node.js, AngularJS)
~
CSS3 \& HTML5
~
Some Java, PHP, MATLAB, \& C
\section{tools}
Git
Grunt
Emacs
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\color{blue}education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--now}
{Bachelor {\normalfont of Natural Sciences}}
{The University of Nottingham, United Kingdom}
{Specialization in Mathematics and Physics}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\color{red}experience}

\begin{entrylist}
\entry
{2013--now}
{Imperial College London}
{London, United Kingdom}
{\emph{Web programming contractor} \\
I built and maintain projectpal.org for Imperial College. The site is used nationally to connect medical students to exciting projects. Used annually by 400 BSc students at Imperial.}
%------------------------------------------------
\end{entrylist}

\section{\color{orange}projects}

\begin{entrylist}
\entry
{}
{ProjectPal.org}
{projectpal.org \& node.projectpal.org}
{\emph{PHP (legacy), M*EAN Stack (*M = MySQL)} \\
Originally written in PHP, I'm now re-implementing it in Node. I used sequelize as an ORM for MySQL. I discovered how useful promises could be while working on this.}
%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{EUPhorics}
{euphorics.herokuapp.com}
{\emph{Node.js, D3.js} \\
Discover European music with this interactive quiz. I used TopoJSON, SVGs, and D3 to make the interactive map.}
%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{PodLearn.com}
{podlearn.herokuapp.com}
{\emph{MEAN Stack} \\
A peer-reviewed platform for medical education podcasts backed by the University of Liverpool.}
%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{Investigation into Semiconductors}
{github.com/tfogo/GaAs-Potentials}
{\emph{MATLAB, C} \\
I built a numerical model of quantum dots formed by the out diffusion of interstitial Mn$^{2+}$ donors in p-type GaAs. The very heavy computational routine was implemented in C for efficiency.}
%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{VoiceCopter}
{github.com/tfogo/voicecopter}
{\emph{Node.js} \\
Control a Parrot AR Drone 2 with voice commands. Work in progress.}
%------------------------------------------------
\end{entrylist}

\section{\color{brown}publications}

{Dipender Gill, Tim Fogarty, Nathan Mountford, Christopher Tang, Elizabeth Yang. \emph{Extra-Curricular Academic Opportunities Amongst Medical Students.} Poster session presented at: National Medical Education Conference; 2013 Jun 1; Exeter, UK.}

\newpage

\section{\color{green}activities}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--now}
{Hack Secretary}
{HackSoc}
{Responsible for finding and advertising external hackathons and organizing transportation to them.}
%------------------------------------------------
\entry
{2012--now}
{Treasurer, Vice-President, and President}
{Public Speaking Society}
{Responsible for leading, running, and financially planning for the society. Responsible for teaching training sessions on public speaking.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\color{purple}interests}

Hackathons, competitive programming (e.g. ICPC, HackerRank, Project Euler), quantum computing, reading A Song of Ice and Fire, running.

\end{document}
